Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-13 WSSSPE4_report/WSSSPE4_paper.tex
more minor shortening

Going into WSSSPE4, the WSSSPE organization had not had a formal mission or vision statement.
The organizers developed a strawhorse, which was presented to the participants early in the meeting.
The presentation included guidelines as well as examples from other similar communities.
The guidelines were that in general, an organization's mission should stand the test of time and state what is wrong and how the organization is going to fix it; its vision should imagine what the world look like if the organization is successful; and from which, focus areas could be use to establish the scope of the organization along with its goals.

@@

\textbf{Definitions:}
\emph{Sustainable software} has the capacity to endure such that it will continue to
be available in the future, on new platforms, meeting new needs.
The \emph{research software lifecycle} includes:
\begin{itemize}
\item acquiring and assembling resources (including funding and people) into teams and communities
\item developing software
\item using software
\item recognizing contributions to and of software
\item maintaining software
\end{itemize}

@@

After most of the lightning talks and other presentations, WSSSPE used three areas of a large room to let
attendees use sticky flip charts and sticky notes on the walls to suggest: (1) a vision on any aspect of the work, (2) a gap or challenge, or (3) a project idea.
Next, attendees organically formed groups around the flip charts on the walls.  This led to the 12 groups that are discussed in the rest of this section.
Summaries of each group's activities follow; for more details
about the group discussions see \cite{WSSSPE4-report}.

>>>>

Going into WSSSPE4, the WSSSPE organization had not had a formal mission or vision statement.
The organizers developed a strawhorse, which was presented to the participants early in the meeting.
The presentation included guidelines as well as examples from other similar communities.
The guidelines were that in general, an organization's mission should stand the test of time and state what the organization does; its vision should imagine what the world look like if the organization is successful; and from which, focus areas could be use to establish the scope of the organization along with its goals.

@@

\textbf{Definitions:}
\emph{Sustainable software} has the capacity to endure such that it will continue to
be available in the future, on new platforms, meeting new needs.
The \emph{research software lifecycle} includes:
acquiring and assembling resources (including funding and people) into teams and communities,
developing software,
using software,
recognizing contributions to and of software,
and
maintaining software.

@@

After most of the lightning talks and other presentations, WSSSPE used three areas of a large room to let
attendees use sticky flip charts and sticky notes on the walls to suggest a vision on any aspect of the work, a gap or challenge, or a project idea.
Next, attendees organically formed groups around the flip charts, and 12 groups emerged.
Summaries of each group's activities follow; for more details
about the group discussions see \cite{WSSSPE4-report}.
